---
title: "interfile"
author: "Kipp Johnson"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Vignette Title}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

# Basic usage

This minimal R package contains (currently) only a single function that can read in binary files stored in the interfile file format as specified by Todd-Pokropek, Cradduck, and Deconinck in "A file format for the exchange of nuclear medicine image data: a specificiation of Interfile version 3.3" (Nuclear Medicine Communications, 13 Sept. 1992, 12(9):673-99)

Interfile file format consists of paired image (file extension: .img) and header (file extension: .hdr) files. The header file is a text file containing a number of key-value pairs, and the image file is a binary file storing pixel intensities in row-major format. Pixel intensities in general correlate to the energy intensity captured by the detector.

We include an example interfile of a bisected rabbit aorta to demonstrate the function.

```{r, Read in an example interfile}
# Load the package
library(interfile)


# Load an example interfile header (Rabbit aorta, Tc99m scan)
interfile.location <-
    system.file("extdata", "Tc99m_20percent_energy.hdr", package = "interfile")

# Read the binary interfile
my_scan <- readHeaderFileHDR(interfile.location)
```

## Plot of data matrix

```{r, fig.show='hold'}
image(my_scan, axes=FALSE, asp=1)
```
